Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-22 main.tex
some progress

We achieve this goal via several auxiliary results. 
We start with a few geometric observations that pertain to the mesh regularity. 
Whenever $T$ is an $n$-dimensional simplex, we define the quantity 
\begin{align*}
    \mu(T)
    := 
    \frac{ \diam(T)^n }{ n! \vol(T) }
    .
\end{align*}
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align*}
    \mu(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \mu(T),
    \qquad 
    \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \kappa(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align*}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\Psi : \Delta^n \rightarrow T$ be an affine diffeomorphism. Then 
    \begin{align*}
        \| \Jacobian \Psi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \Psi^{-1} \|
        \leq 
        \sqrt{2n^n} 
        % \frac{ n! \vol(T) } { \diam(T)^n }
        \mu(T)^{-1}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Psi$ in descending order.
    Then $\sigma_1/\sigma_n \leq \sigma_1^n / \det(\Jacobian\Psi)$. Hence 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1^n }{ \det(\Jacobian\Psi) } 
        \sigma_n
        \leq 
        \sqrt{2n^n} 
        \frac{ \diam(T)^n }{ n! \vol(T) } 
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        &\leq 
        \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
        \cdot 
        \frac{\diam(T_2)^n}{n! \vol(T_2)} 
        \leq 
        \mu(T_1) \mu(T_2)
        ,
        \\
        \diam(T_1)
        &\leq 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \diam(F)
        \leq 
        \mu(T_1)
        \diam(F)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \mu(T_1) }{ \mu(T_2) }
        .
    \end{align*}
\end{lemma}
\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(F)
        .
    \end{align*}
    The first estimate follows. 
    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
    \begin{align*}
        \diam(F)
        \geq 
        h
        =
        n!
        \frac{ \vol(T_1) }{ \vol(F') }
        \geq 
        \frac{ n! \vol(T_1) }{ \diam(T_1)^n }
        \cdot 
        \diam(T_1)
        .
    \end{align*}
    That shows the second estimate. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \sqrt{n} 
        \cdot 
        \diam(T_1)
        \sqrt{2n^n} 
        \frac{ n! \vol(T_2) } {\diam(T_2)^n } 
        \diam(T_2)^{-1}
        \\&
        \leq 
        \sqrt{n} 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \diam(F)
        \sqrt{2n^n} \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        \diam(F)^{-1}
        \leq 
        \sqrt{2n^{n+1}}
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        .
    \end{align*}
    All the desired results thus follow. 
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^n}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

\begin{remark}
    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\mu(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \left( 
            \frac{\diam(T_1)^n}{n! \vol(T_1)} 
            \frac{\diam(T_2)^n}{n! \vol(T_2)} 
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
\begin{proof}
    Let $\hat T_1$ be the $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
    We fix affine homeomorphisms $\Phi_1 : \hat T_1 \rightarrow T_1$ and $\Phi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with finite triangulation $\calT$.
    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
    there exists a strong path $T_0, T_1, \dots, T_m = T$.
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
    and such that for all $T \in \calT$:
    \begin{align*}
        \| w_{m} \|_{L^{p}(T_m)}^{p}
        &\leq 
        (m+1)^{p-1}
        \sum_{t=1}^{m} 
        \left( 
            \prod_{t < l \leq m} 
            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
        \right)
        \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{p/q}
        C_{p,T_{t} \cup T_{t+1}}
        \| \nabla u \|_{L^{p}( T_{t} \cup T_{t+1} )}^{p}
        \\&\quad \quad \quad 
        +
        (m+1)^{p-1}
        \left( 
            \prod_{0 < l \leq m} 
            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
        \right)
        C_{p,T_{0}}
        \| \nabla u \|_{L^{p}(T_{0})}^{p}
        .
    \end{align*}
\end{theorem}

@@

 We want to summarize the two integrals of $u_{F_m}$. 

@@

\begin{lemma}\label{lemma:mixedbconsimplex}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,p} \diam(T) \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where 
    \begin{align*}
        C_{\partial,p}
        \leq 
        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right) 
        .
    \end{align*}
    % \begin{align*}
    %     \| u \|_{L^{p}(T)}
    %     &
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla w \|_{\bfL^{p}(T)}
    %     +
    %     \| \gamma \|_{\bfL^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T)
    %     \| \nabla w \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} 
    %     \diam(T) \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     .
    % \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{{\rm PF},T,p} 
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
        \diam(T)^{p}
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The desired result follows. 
\end{proof}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with finite triangulation $\calT$.
    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
    there exists a strong path $T_0, T_1, \dots, T_m = T$.
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
    and such that for all $T \in \calT$:
    \begin{align*}
        \| w_{m} \|_{L^{p}(T_m)}^{p}
        &\leq 
        (m+1)^{p-1}
        \sum_{t=1}^{m} 
        \left( 
            \prod_{t < l \leq m} 
            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
        \right)
        \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{p/q}
        C_{{\rm PF},T_{t} \cup T_{t+1},p}
        \| \nabla u \|_{L^{p}( T_{t} \cup T_{t+1} )}^{p}
        \\&\quad \quad \quad 
        +
        (m+1)^{p-1}
        \left( 
            \prod_{0 < l \leq m} 
            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
        \right)
        C_{{\rm PF},T_{0},p}
        \| \nabla u \|_{L^{p}(T_{0})}^{p}
        .
    \end{align*}
    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
\end{theorem}

@@

\section{Extension operator on finite element stars}

>>>>

Towards this goal, we introduce quantitative measures for the geometric quality of triangulations,
which give an indication of the regularity of simplex shapes. 
Most of such \emph{shape measures} in the literature are based on geometric features, 
but we consider indicators based on affine transformations associated with the mesh;
this is because the properties of these transformations are what shows up in our estimates.

Whenever $T$ is an $n$-dimensional simplex 
\begin{align*}
    \kappa(T)
    := 
    \frac{ \diam(T)^n }{ n! \vol(T) }
    .
\end{align*}
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align*}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align*}
Whenever $S,T$ are two $n$-simplices that are a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align*}
    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
\end{align*}
This indicator quantifies how much reflection across the shared face distorts the goemetry.

% and $\Phi : \Delta^n \rightarrow T$ is an affine diffeomorphism from the reference simplex,
% we define the quantity 
% \begin{align*}
%     \kappa(T)
%     := 
%     \frac{ \diam(T)^n }{ n! \vol(T) }
%     .
% \end{align*}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\Phi : \Delta^n \rightarrow T$ be an affine diffeomorphism. Then 
    \begin{align*}
        \| \Jacobian \Phi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \Phi^{-1} \|
        \leq 
        \sqrt{2n^n} 
        % \frac{ n! \vol(T) } { \diam(T)^n }
        \kappa(T)^{-1}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Phi$ in descending order.
    Then $\sigma_1/\sigma_n \leq \sigma_1^n / \det(\Jacobian\Phi)$. Hence 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1^n }{ \det(\Jacobian\Phi) } 
        \sigma_n
        \leq 
        \sqrt{2n^n} 
        \frac{ \diam(T)^n }{ n! \vol(T) } 
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        &\leq 
        \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
        \cdot 
        \frac{\diam(T_2)^n}{n! \vol(T_2)} 
        \leq 
        \kappa(T_1) \kappa(T_2)
        ,
        \\
        \diam(T_1)
        &\leq 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \diam(F)
        \leq 
        \kappa(T_1)
        \diam(F)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
\end{lemma}
\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(F)
        .
    \end{align*}
    The first estimate follows. 
    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
    \begin{align*}
        \diam(F)
        \geq 
        h
        =
        n!
        \frac{ \vol(T_1) }{ \vol(F') }
        \geq 
        \frac{ n! \vol(T_1) }{ \diam(T_1)^n }
        \cdot 
        \diam(T_1)
        .
    \end{align*}
    That shows the second estimate. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \sqrt{n} 
        \cdot 
        \diam(T_1)
        \sqrt{2n^n} 
        \frac{ n! \vol(T_2) } {\diam(T_2)^n } 
        \diam(T_2)^{-1}
        \\&
        \leq 
        \sqrt{n} 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \diam(F)
        \sqrt{2n^n} \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        \diam(F)^{-1}
        \leq 
        \sqrt{2n^{n+1}}
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        .
    \end{align*}
    All the desired results thus follow. 
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^n}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

\begin{remark}
    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \rho(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
\begin{proof}
    Let $\hat T_1$ be the $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
    We fix affine homeomorphisms $\Phi_1 : \hat T_1 \rightarrow T_1$ and $\Phi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly-connected finite triangulation $\calT$.
    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
    we fix a strong path $T_0, T_1, \dots, T_m = T$.
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
    and such that for all $T \in \calT$:
    \begin{align*}
        \| w_{m} \|_{L^{p}(T_m)}^{p}
        &\leq 
        (m+1)^{p-1}
        \sum_{t=1}^{m} 
        \left( 
            \prod_{t < l \leq m} 
            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
        \right)
        \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{p/q}
        C_{p,T_{t} \cup T_{t+1}}
        \| \nabla u \|_{L^{p}( T_{t} \cup T_{t+1} )}^{p}
        \\&\quad \quad \quad 
        +
        (m+1)^{p-1}
        \left( 
            \prod_{0 < l \leq m} 
            \frac{ \vol(T_l) }{ \vol(T_{l-1}) } 
        \right)
        C_{p,T_{0}}
        \| \nabla u \|_{L^{p}(T_{0})}^{p}
        .
    \end{align*}
\end{theorem}

@@

 We summarize the two integrals of $u_{F_m}$. 
 % 

@@

\begin{lemma}\label{lemma:mixedbconsimplex}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,p} \diam(T) \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where $C_{\partial,p} > 0$ is a constant such that 
    \begin{align*}
        C_{\partial,p}
        \leq 
        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right),  
        \quad 
        C_{\partial,p}
        \leq 
        2^{\frac n p}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{{\rm PF},T,p} 
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
        \diam(T)^{p}
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The first inequality follows.

    There exists $\Phi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
    We let $\hat u := u \circ \Phi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Phi )$. 
    Then $\nabla \hat u = \hat g$. 
    % 
    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordinate axes.
    We define $\tilde g = \nabla \tilde u$
    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
    \begin{gather*}
        \| \tilde u \|_{L^{p}(\hat U)} 
        \leq 
        2 
        \| \tilde g \|_{\bfL^{p}(\hat U)}
        .
    \end{gather*}
    In addition to that, 
    \begin{gather*}
        \| u \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Dif \Phi)|^{\frac 1 p} 
        \| \hat u \|_{L^{p}(\hat T)}
        \leq 
        |\det(\Dif \Phi)|^{\frac 1 p} 
        \| \tilde u \|_{L^{p}(\hat U)}
        ,
        \\
        \| \tilde g \|_{\bfL^{p}(\hat U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{\bfL^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Dif \Phi_1)|^{-\frac 1 p} \| \Dif \Phi \| \cdot 
        \| \nabla u \|_{\bfL^{p}(T)}
        .
    \end{gather*}
    The second inequality follows.
\end{proof}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:gradzwei}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly connected finite triangulation $\calT$.
    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
    we fix a strong path $T_0, T_1, \dots, T_m = T$.
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
    and such that for all $T \in \calT$:
    \begin{align*}
        \| w_{m} \|_{L^{p}(T_m)}
        &\leq 
        \sum_{l=1}^{m} 
        \rho(\calT)^{\frac{m-l}{p}}
        C_{{\rm PF},T,p} \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) \diam(T_{0})
        \| \nabla u \|_{L^{p}( T_{l} )}
        +
        \rho(\calT)^{\frac m p}
        C_{{\rm PF},T_{0},p} \diam(T_{0})
        \| \nabla u \|_{L^{p}( T_{0} )}
        .
    \end{align*}
    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
\end{theorem}

@@
